Data Appendix to "The impact of weather events on schooling outcomes

### 2020-05-01 data_appendix_all_years.Rmd
commiting final changes, intermediate draft to go back to

@@

reg_data <- total_subset %>%
  mutate(year_factor = as.factor(year),
         lny = log(income))

@@

#model_simple <- lm(assist ~ floods + droughts + year, data = reg_data)
#summary(model_simple)
#model_assist <- lm(assist ~ floods + droughts + age + female + income + child + grandchild + num_children + hhhead_educ + female_hhhead + rural + year_factor, data = reg_data)
#summary(model_assist)
#model_register <- lm(register ~ floods + droughts + age + female + income + child + grandchild + num_children + hhhead_educ + female_hhhead + rural + year_factor, data = reg_data)
#summary(model_register)
model_reason_t <- (lm(work_reason ~ floods + droughts + age + female + income + child + grandchild + num_children + hhhead_educ + female_hhhead + year_factor, data = reg_data))
summary(model_reason_t)

@@

```{r generate regression table, echo = F, results = "asis"}
stargazer::stargazer(list(model_assist_r, model_register_r), 
               title = "Full sample regression results", 
               label = "fullResults",
               header = F,
               keep = c("floods", "droughts"))
```
```{r probit regression total sample}

@@

>>>>

---
output:
  pdf_document: default
  html_document: default
---

@@

reg_data <- total_subset %>%
  mutate(year_factor = as.factor(year),
         income2 = case_when(income == 0 ~ 1), 
         lny = log(income2))

@@

#model_simple <- lm(assist ~ floods + droughts + year, data = reg_data)
#summary(model_simple)
model_assist <- lm(assist ~ floods + droughts + age + female + lny + child + grandchild + num_children + hhhead_educ + female_hhhead + rural + year_factor, data = reg_data)
summary(model_assist)
model_register <- lm(register ~ floods + droughts + age + female + lny + child + grandchild + num_children + hhhead_educ + female_hhhead + rural + year_factor, data = reg_data)
summary(model_register)
model_reason_t <- (lm(work_reason ~ floods + droughts + age + female + lny + child + grandchild + num_children + hhhead_educ + female_hhhead + year_factor, data = reg_data))
summary(model_reason_t)

@@

```{r generate regression table, echo = F, results = "asis"}
stargazer::stargazer(list(model_assist, model_register), 
               title = "Full sample regression results", 
               label = "fullResults",
               header = F,
               keep = c("floods", "droughts"))
```
```{r probit regression total sample}

@@

```{r generate probit regression table, echo = F, results = "asis"}
stargazer::stargazer(list(probitMod_assist, probitMod_register, probitMod_work), 
               title = "Full sample probit regression results", 
               label = "fullResults",
               header = F,
               keep = c("floods", "droughts"))
